Opportunities and precautions for the use of MPAs in bycatch reduction

### 2022-08-17 documents/03_marlin_paper.Rmd
haev functional results with DAT movement

---
title: "Opportunities and precautions for the use of MPAs in bycatch reduction"
author:
    - Daniel Ovando
    - Darcy Bradley
    - Lennon Thomas
    - Echelle Burns
date: "`r Sys.Date()`"
output: 
  bookdown::word_document2:
    number_sections: false
    reference_docx: template.docx
  bookdown::html_document2: default
  bookdown::pdf_document2:
    number_sections: false
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
bibliography: references.bib
params:
  run_name: ["v1.1"]
csl: proceedings-of-the-royal-society-b
---

@@

capitalize <- function(string) {
  substr(string, 1, 1) <- toupper(substr(string, 1, 1))
  string
}

@@

@@

worst_result_plot <- worst_result %>%
  ggplot() +
  geom_text(data = tibble(
    x = .1,
    y = max(worst_result$biodiv - worst_result$bau_biodiv)
  ),
  aes(x = x, y = y, label = "Worst Case"),
  size = 4) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_line(aes(prop_mpa, biodiv - bau_biodiv, color = critter),
            show.legend = FALSE, size = 1.25) +
  scale_x_continuous(labels = scales::percent, name = "MPA Size") +
  scale_y_continuous(
    name = ''
  )

@@

best_result_plot <- best_result %>%
  ggplot() +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_line(aes(prop_mpa, biodiv - bau_biodiv, color = critter), size = 1.25) +
  geom_text(data = tibble(
    x = .1,
    y = max(best_result$biodiv - best_result$bau_biodiv)
  ),
  aes(x = x, y = y, label = "Best Case"),
  size = 4) +
  scale_x_continuous(labels = scales::percent, name = "") +
  scale_y_continuous("Change in SSB/SSB0") +
  theme(legend.position = "top") +
  scale_color_discrete(name = element_blank()) +
  labs(title = "A) ")

>>>>

---
title: "Opportunities and precautions for the use of MPAs in bycatch reduction"
author:
    - Daniel Ovando
    - Darcy Bradley
    - Lennon Thomas
    - Echelle Burns
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    number_sections: false
  bookdown::html_document2: default
  bookdown::word_document2:
    number_sections: false
    reference_docx: template.docx
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
bibliography: references.bib
params:
  run_name: ["v1.1"]
csl: proceedings-of-the-royal-society-b
---

@@

@@

- Include partial dependency plots for variable importance plot

@@

worst_result_plot <- worst_result %>%
  ggplot() +
  geom_text(data = tibble(
    x = .1,
    y = max(worst_result$biodiv - worst_result$bau_biodiv) * .9
  ),
  aes(x = x, y = y, label = "Worst Case"),
  size = 4) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_line(aes(prop_mpa, biodiv - bau_biodiv, color = critter),
            show.legend = FALSE, size = 1.25) +
  scale_x_continuous(labels = scales::label_percent(accuracy = 1), name = "MPA Size") +
  scale_y_continuous(
    name = ''
  )

@@

best_result_plot <- best_result %>%
  ggplot() +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_line(aes(prop_mpa, biodiv - bau_biodiv, color = critter), size = 1.25) +
  geom_text(data = tibble(
    x = .1,
    y = max(best_result$biodiv - best_result$bau_biodiv) * .9
  ),
  aes(x = x, y = y, label = "Best Case"),
  size = 4) +
  scale_x_continuous(labels = scales::label_percent(accuracy = 1), name = "") +
  scale_y_continuous("Change in SSB/SSB0") +
  theme(legend.position = "top") +
  scale_color_discrete(name = element_blank()) +
  labs(title = "A) ")
